\subsection*{Part b - Randomized algorithm}

\subsubsection*{Input}

$V \in \mathbb{R}_{_{\geq 0}}^n$, with exactly $d \in [1..n]$ non-zero elements, accuracy parameter $\delta$.

\subsubsection*{Output}

Returns an index $i$ with $V[i] \neq 0$ with probability of at least $1 - \delta$.

\subsubsection*{Algorithm}

If d = 1: run deterministic algorithm on $V$

Otherwise:
\begin{itemize}
    \item Repeat $k$ times:
    \begin{enumerate}
        \item For $i \in [1..n]$: Draw $x_i \in \{0, 1\}$ with $\Pr[x_i = 1] = \frac{1}{d}$ 
        
        \item Let $W = [V[0]\cdot x_0,\dots,V[n] \cdot x_n ]^T$
        
        \item If $Q_W([1..n]) \neq 0$:
                
        \begin{itemize}
            \item Run deterministic algorithm on $W$
            
            \item If index is returned by deterministic algorithm: return index
            
        \end{itemize}
        
    \end{enumerate} 
    
    \item return $0$
\end{itemize} 

Where $k = 9 \cdot \log(1/\delta)$ and $Q_W(S) = \sum_{j \in S} W[j]$ is the summation query over vector $W$

\subsubsection*{Run time}

If $d = 1$, the algorithm runs in $\bigO(\log n)$.

Otherwise, one iteration of the algorithm performs one summation query plus at most $\bigO(\log n)$ summation queries by calling the deterministic algorithm.

Thus, one iteration performs $\bigO(\log n)$ summation queries.

By repeating $k \in \bigO(\log(1/\delta))$ times, the total number of summation queries is in  $\bigO(\log(n)\cdot\log(1/\delta))$.

\subsubsection*{Correctness}

\begin{itemize}
    \item Case $d = 1$:
    
    The algorithm executes the deterministic algorithm. All necessary input conditions are met.

    Thus, correctness follows from correctness of deterministic algorithm. The probability of returning the correct index is $1$ and therefore at least $1 - \delta$.
    
    
    \item Case $d \neq 1$
    
    \underline{Analyzing one iteration:}
    
    \textit{Claim:} $W$ contains exactly one non-zero element with probability $p \geq \frac{1}{4}$
    
    \textit{Proof:} 
    
    Every index with a zero element in $V$ is also an index with a zero element in $W$ by construction of $W$.
    
    Therefore, only non-zero elements of $V$ might remain in $W$. By construction, each of the $d$ non-zero element remains in $W$ with probability $\frac{1}{d}$. Let $X$ be the amount of non-zero elements remaining in $W$.
    
    $X \sim \operatorname{Binomial}\left(d, \frac{1}{d}\right)$
    
    $\Pr[X = 1] = 
    {d \choose 1} \cdot \frac{1}{d} \cdot \left(1 - \frac{1}{d}\right)^{d-1} = 
    \left(1 - \frac{1}{d}\right)^{d-1} =
    \frac{\left(1 - \frac{1}{d}\right)^{d} }{1 - \frac{1}{d}} \geq
    \frac{\left(1 - \frac{1}{d}\right)^{d} }{1 - 0} = 
    \left(1 - \frac{1}{d}\right)^{d} 
    $ 
    
    Since $d \in [1..n]$ and $d \neq 1$: $d \geq 2$ 

    For $d = 2$: $\left(1 - \frac{1}{d}\right)^{d} = \frac{1}{4}$
        
    The term $\left(1 - \frac{1}{d}\right)^{d}$ is monotonically increasing as $d$ increases (see calculus).  
    
    Thus, $\left(1 - \frac{1}{d}\right)^{d} \geq \frac{1}{4}$
    
    $\Rightarrow \Pr[X = 1] \geq \frac{1}{4}$
    
    \textit{q.e.d}
    
    The if condition ensures, that $W$ contains at least one non-zero element.
    
    Therefore, the input conditions for the deterministic algorithm are met. 
    
    Whenever $W$ contains exactly one non-zero element, the correct index of that element is returned by the deterministic algorithm. Otherwise, a string is returned.
    
    By construction of $W$, this index is also a valid non-zero index in the original vector. Hence, the entire algorithm succeeds and returns a valid index.
    
    The probability of $W$ containing exactly one non-zero element is $p \geq \frac{1}{4}$. Thus, one iteration succeeds with $p \geq \frac{1}{4}$.
    
    \underline{After $k$ iterations}
    
    The algorithm returns a correct element whenever one iteration returns.
    
    The algorithm can only fail, if no valid index was found within $k$ iterations, i.e. if every iteration fails.
    
    $\Rightarrow \Pr[\textit{error}] \leq 
    (1 - p)^k \leq 
    \left(1 - \frac{1}{4}\right)^k = 
    \left(\frac{3}{4}\right)^k = 
    e^{k \cdot \log(3/4)} = $
    
    $ = e^{9 \cdot \log(1/\delta) \cdot \log(3/4)} \leq
    e^{\frac{- 1}{\log(3/4)} \cdot \log(1/\delta) \cdot \log(3/4)} = 
    e^{-\log(1/\delta)} = 
    e^{\log \delta} =
    \delta$
    
    $\Rightarrow \Pr[\textit{success}] = 1 - \Pr[\textit{error}] \geq 1 - \delta$
    
\end{itemize}

